Porting the Steel Bank Common Lisp Compiler and Runtime to the Nintendo Switch NX Platform

### 2025-04-09 els2025-sbcl-nx/paper.tex
Punctuation.
More detailed captions.

\end{minted}
\caption{A Lisp function referencing the constants \code{'(42 . 1958)} and \code{'ELS2025}}
\label{lst:function}
\end{listing}

@@

\begin{figure}[h]
  \label{fig:before-shrinkwrap}
  \centering
  \includesvg[width=\linewidth]{Code object before shrinkwrapping.drawio.svg}
  \caption{Representation of the compiled code object for the function
    \protect\texttt{\#'f}.}
\end{figure}

@@

\begin{figure}[h]
  \label{fig:after-shrinkwrap}
  \centering
  \includesvg[width=\linewidth]{Code objects in memory after shrinkwrapping.drawio.svg}
  \caption{Representation of the same code object after code/data
    segregation.}
\end{figure}

>>>>

\end{minted}
\caption{A Lisp function referencing the constants \code{'(42 . 1958)} and \code{'ELS2025}.}
\label{lst:function}
\end{listing}

@@

\begin{figure}[h]
  \label{fig:before-shrinkwrap}
  \centering
  \includesvg[width=\linewidth]{Code object before shrinkwrapping.drawio.svg}
  \caption{Representation of the compiled code object (in boldface)
    for the function \protect\texttt{\#'f} in memory, along with the
    cons and symbol objects it references.}
\end{figure}

@@

\begin{figure}[h]
  \label{fig:after-shrinkwrap}
  \centering
  \includesvg[width=\linewidth]{Code objects in memory after shrinkwrapping.drawio.svg}
  \caption{Representation of the same code object and the cons and
    symbol objects it references after code/data segregation and the
    rest of the shrinkwrapping process.}
\end{figure}
